Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
wibbles and comment in intro

Among the mechanisms that should be amenable to making strong formal guarantees,
Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies~\cite{pump_oakland2015} for stack safety.
Their most realistic micro-policy, ``Lazy Tagging and Clearing'' (\(LTC\)),
makes an interesting trade-off for performance: it allows function activations to write
into one another's stack frames, but ensures that the owner of the corrupted memory cannot access
it afterward. Because the memory does get corrupted, \(LTC\) would not fulfill an
adaptation Georges et al.'s property to the tagged setting.

Neverthess, we believe that there is a useful sense in which \(LTC\) does (attempt to) enforce stack safety. 
It does not always protect individual addresses on the stack, but it tries to 
prevent one function activation from interfering with another's behavior---protecting 
the functional abstraction, which we argue is the real essence of stack safety.

@@

\paragraph*{Towards Formal Properties for Stack Safety}

>>>>

Among the mechanisms that should be amenable to making strong formal guarantees,
Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies~\cite{pump_oakland2015} for stack safety.
Their most realistic micro-policy, ``Lazy Tagging and Clearing'' (\(LTC\)),
makes an interesting trade-off for performance: it allows function activations to write
into one another's stack frames, but ensures that the owner of the corrupted memory cannot access
it afterward. Because the memory does get corrupted, \(LTC\) would not fulfill an
adaptation of Georges et al.'s property to the tagged setting.

Neverthess, we believe that there is a useful sense in which \(LTC\) does (attempt to) enforce stack safety. 
While it does not always protect individual addresses on the stack, it tries to 
prevent one function activation from interfering with another's behavior---protecting 
the functional abstraction, which we argue is the real essence of stack safety.

@@

\subsection {Towards Formal Properties for Stack Safety}

\apt{Too much real estate to sell the generality, flexibility, etc. of our approach.
  Again, we are not providing evidence that these attributes are true, although we can
  and should conjecture claim them in passing.}
